### 2017-05-12 abstract1.tex
...

\centerline{\hei\xiaoerhao 摘\quad 要}
\vspace{0.5cm}
本体的构建是知识库研究的一个基础，构建本体需要获取领域相关的知识，并对领域相关知识进行一致化的描述，目的是能够给出领域内一致的词汇术语以及能够描述词汇术语间相互关系的规则。在有效存储信息的基础上，能够实现术语和公理预测、问答查询等推理任务。目前，已经有一部分的工作集中在本体的自动化和半自动化构建的研究中，然而目前的情况是知识库的不完善难以避免，导致某些符合客观事实的公理无法被正确的蕴含。本文的主要工作，是利用本体中溯因推理的技术找出这些观察值无法被正确蕴含的原因，并计算出合乎语义的解释对知识库进行修复。

>>>>

\centerline{\hei\xiaoerhao 摘\quad 要}
\vspace{0.5cm}
本体的构建是知识库研究的一个基础，构建本体需要获取领域相关的知识，并对领域相关知识进行一致化的描述，目的是能够给出领域内一致的词汇术语以及能够描述词汇术语间相互关系的规则。在有效存储信息的基础上，能够实现术语和公理预测、问答查询等推理任务。目前，已经有一部分的工作集中在本体的自动化和半自动化构建的研究中，然而目前的情况是知识库的不完善难以避免，导致某些符合客观事实的公理无法被正确的蕴含。本文的主要工作，是利用本体中溯因推理的技术找出这些观察值无法被正确蕴含的原因，并基于决断集模板提出了一套完整的本体溯因诊断框架。

### 2017-05-12 abstract2.tex
...

The construction of ontology is a foundation of knowledge base research. Constructing ontology needs to acquire domain-related knowledge and describe the domain-related knowledge in order to give consistent vocabulary terms in the field and the rules to describe the relationship between vocabulary terms. On the basis of effective storage of information, to achieve the terminology and axiom prediction, question and answer inquiries and other reasoning tasks. At present, part of the work has focused on the study of ontology automation and semi-automatic construction. However, the current situation is that the imperfections of the knowledge base are difficult to avoid, and some axioms that conform to the objective facts can not be correctly implied. The main work of this paper is to use the technique of ontology inversion to find out why these observations can not be correctly entailed, and to calculate the semantic explanations of the knowledge base to repair.

>>>>

The construction of ontology is a foundation of knowledge base research. Constructing ontology needs to acquire domain-related knowledge and describe the domain-related knowledge in order to give consistent vocabulary terms in the field and the rules to describe the relationship between vocabulary terms. On the basis of effective storage of information, to achieve the terminology and axiom prediction, question and answer inquiries and other reasoning tasks. At present, part of the work has focused on the study of ontology automation and semi-automatic construction. However, the current situation is that the imperfections of the knowledge base are difficult to avoid, and some axioms that conform to the objective facts can not be correctly implied. The main work of this paper is to use the technique of ontology inversion to find out why these observations can not be correctly entailed, and based on the justification pattern, a complete set of ontological diagnosis framework is proposed.

### 2017-05-12 chap2.tex
...

			$$
				\begin{aligned}
				Person(\mathsf{Mary})
				\end{aligned}
				$$
			 又根据$\exists giveBirth.Person \sqsubseteq Female$，$giveBirth(\mathsf{Lily}, \mathsf{Mary})$以及个体断言$Person(\mathsf{Mary})$，我们可以得到：
			$$
				\begin{aligned}
				Female(\mathsf{Lily})
				\end{aligned}
				$$
			 令：
			 	$$ \mathcal{S}=\left\{
				\begin{aligned}
				giveBirth(\mathsf{Lily}, \mathsf{Mary})\\
				Female(\mathsf{Mary})\\
				\exists giveBirth.Person \sqsubseteq Female\\
				Female \sqsubseteq Person\\
				\end{aligned}
				\right\}.
				$$

@@

    \begin{definition}[术语断言溯因诊断解释)]
        令$\mathcal{L}_S$为一个DL本体，且$A$为一个多个在$\mathcal{L}_S$中的术语断言集合。对于一个溯因诊断问题$\langle \mathcal{K}, \Phi \rangle$，当且仅当$\mathcal{K} \cup A \vDash \Phi$我们把$A$称为可接受解释。更多的，我们把$A$称为：
        \begin{enumerate}
               \item $(\emph{一致})$ 当且仅当$\mathcal{K} \cup A \nvDash \bot$。
               \item $(\emph{非平凡})$ 当且仅当 $\mathcal{K} \nvDash \Phi$。
               \item $(\emph{最小})$ 当且仅当不存在对于$\langle \mathcal{K}, \Phi \rangle$问题的解释$B$，其中$B$是$A$的实例化子集。我们说$B$是$A$的实例化子集当且仅当存在一个重命名映射$\rho$:$N_I^*(B) \mapsto N_I^*(A)$，其中$N_I^*(B)$和$N_I^*(A)$是来自于$A$和$B$的个体名且不出现于$\mathcal{K}$，使得$A \vDash \rho B$。但是对于所有的$\varrho$:$N_I^*(A) \mapsto N_I^*(B)$满足$B \nvDash \varrho A$。满足以上条件的，我们称$A$是问题$\langle \mathcal{K}, \Phi \rangle$的最小解释。
        \end{enumerate}

@@

	考虑以下例子：
	\begin{example}
		令$\mathcal{O} = \mathcal{T} \cup \mathcal{A}$是一个DL 本体，其中TBox $\mathcal{T}$和ABox $\mathcal{A}$包含以下公理：

>>>>

			$$
				\begin{aligned}
				Person(\mathsf{Mary})
				\end{aligned}
				$$
			 又根据$\exists giveBirth.Person \sqsubseteq Female$，$giveBirth(\mathsf{Lily}, \mathsf{Mary})$以及个体断言 $Person (\mathsf{Mary})$，我们可以得到：
			$$
				\begin{aligned}
				Female(\mathsf{Lily})
				\end{aligned}
				$$
			 令：
			 	$$ \mathcal{S}=\left\{
				\begin{aligned}
				giveBirth(\mathsf{Lily}, \mathsf{Mary})\\
				Female(\mathsf{Mary})\\
				\exists giveBirth.Person \sqsubseteq Female\\
				Female \sqsubseteq Person\\
				\end{aligned}
				\right\}.
				$$

@@

    \begin{definition}[术语断言溯因诊断解释)]
        令$\mathcal{L}_S$为一个DL本体，且$A$为一个多个在$\mathcal{L}_S$中的术语断言集合。对于一个溯因诊断问题$\langle \mathcal{K}, \Phi \rangle$，当且仅当$\mathcal{K} \cup A \vDash \Phi$我们把$A$称为可接受解释。更多的，我们把$A$称为：
        \begin{enumerate}
               \item $(\emph{一致})$ 当且仅当$\mathcal{K} \cup A \nvDash \bot$。
               \item $(\emph{非平凡})$ 当且仅当 $\mathcal{K} \nvDash \Phi$。
               \item $(\emph{最小})$ 当且仅当不存在对于$\langle \mathcal{K}, \Phi \rangle$ 问题的解释$B$，其中$B$是$A$的实例化子集。我们说$B$是$A$的实例化子集当且仅当存在一个重命名映射$\rho$:$N_I^*(B) \mapsto N_I^*(A)$，其中$N_I^*(B)$和$N_I^*(A)$是来自于$A$和$B$的个体名且不出现于$\mathcal{K}$，使得$A \vDash \rho B$。但是对于所有的$\varrho$:$N_I^*(A) \mapsto N_I^*(B)$满足$B \nvDash \varrho A$。满足以上条件的，我们称$A$是问题$\langle \mathcal{K}, \Phi \rangle$的最小解释。
        \end{enumerate}

@@

	考虑以下例子：
	\begin{example}
		令$\mathcal{O} = \mathcal{T} \cup \mathcal{A}$是一个DL 本体，其中TBox $\mathcal{T}$ 和ABox $\mathcal{A}$包含以下公理：
